---
title: "Getting Sophisticated"
output:
  html_document:
    toc: true
    toc_float: true
---

**First off**, note that 

1. there is a table of contents, and 
1. it is floating
1. also note that my numbering in this list renders nicely


## With R code

You can execute R code each time you build your website. 

### in line

Today's date is `r Sys.Date()`. It is  

### in a chunk

Plot of cars

```{r plot cars}
plot(cars)
plot(iris3)
```

### with `_site.R`

```{r setup, echo=F, warning=FALSE, message=F}
source("./advanced/_site.R")
```
 
## Styling

Disclaimer: Most of what is here I figured out through googling and trial and error...so there are most definitely better and more elegant ways to do this. But here are some ideas: 

### figures
sizing, centering, 

### columns
 
<!---From http://stackoverflow.com/questions/31753897/2-column-section-in-r-markdown:
Put in your css file or directly in rmarkdown--->
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>
 
<br> 
**Global Ocean Health Index assessments score 10 goals, some of which have sub-goals**. Here you will find a description about how goals are represented in global assessments. Goal-by-goal, you can explore the data used to model status and trend, as well as the pressures and resilience measures contributing to goal scores.     

![](https://docs.google.com/drawings/d/17N97_cydibY4QM79tnVf-hLDii0NNm3VhBJ2hhkKKkM/pub?w=1344&h=192)

----

-----

<div class="col2">
**Column 1**

- note `<div class="col2">` and `</div>`
- what beautiful bullet points
<br>
<br>

**Column 2**

- I have 3 bullet points here
- which means to align with the left column
- I added a `<br>` there
</div>

<br>

<center>
**Here the text is centered**

• [2016 Global OHI Scores Report](https://github.com/OHI-Science/ohi-science.github.io/raw/master/assets/downloads/other/2016_Global_OHI_Scores_Report_compressed.pdf) • [Peer-reviewed publications](http://ohi-science.org/resources/publications/) • 
</center>

---- 


### colored text

## Templates/themes

### troubleshooting

If when running `rmarkdown::render_site()` you get this error: 

```{r}
# Error in object[seq_len(ile)] : 
#  object of type 'symbol' is not subsettable


```
Go to *Session > Restart R* and try again. 

  

