---
title: "Making free websites with RStudio's R Markdown"
author:  "[Julie Lowndes](https://github.com/jules32) at [NCEAS](https://www.nceas.ucsb.edu/), 12/14/16"
output:
  html_document:
    fig_width: 1
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>

----

It's possible to create well-designed websites for free using [RStudio's R Markdown](http://rmarkdown.rstudio.com/) and hosting them on [Github](http://github.com). This is very new and incredibly cool. It is a really powerful way to communicate science using the same reproducible workflow you use for your analyses and collaborations.

***Creating websites with R Markdown can be done without knowing R or HTML, CSS, etc,*** and that's where we'll start. However, R Markdown integrates with these tools so the more you know the more complex and beautiful your website can be; we'll see examples of that too. 

The best way to learn is to follow along with your own laptop, but all are welcome. We'll spend half the time with the tutorial and half the time for you to work on your own website and get help. If you bring your laptop please do this beforehand: 

1. install RStudio
1. create a [GitHub]((http://github.com)) account ([advice](http://happygitwithr.com/github-acct.html))
1. set up your computer to talk to GitHub
    - have RStudio linked directly (preferred) ([instructions sections 8-14](http://happygitwithr.com/hello-git.html))
    -or install the [Desktop App](https://desktop.github.com/)
    - or be familiar with git commands for the command line ([tutorial](https://try.github.io/levels/1/challenges/1))

----

<div class="col2">

```{r fig.width=4, fig.height=4,echo=FALSE}
library(png)
library(grid)
img <- readPNG('images/flower_GLOBAL_2016.png')
grid.raster(img)
```

<br>
<br>
<br>
**Examples:**

We have been using R Markdown for the Ocean Health Index. We created [ohi-science.org/ohi-global](http://ohi-science.org/ohi-global) with R Markdown alone.  
Before R Markdown could make websites (i.e. a few months ago), we built websites using a similar workflow (and Jekyll). This is how Lauren Walker created [ohi-science.org](http://ohi-science.org) and I created [my personal website](http://jules32.github.io/) (we'll be simplifying these in the future to work just with R Markdown).  
And R Markdown is much more than just websites -- here's a [one-minute video about R Markdown](http://rmarkdown.rstudio.com/lesson-1.html) to get you excited. 
</div>
